\speculake: Hiding Malware in Speculative Execution

### 2018-05-08 paper/payloads.tex

\subsection{Virtual Machines}
We demonstrate in Section~\ref{subsec:turing} that general purpose computation 
is possible in the speculative environment in spite of the constraints 
imposed by the speculative world. However, a Turing Machine
is not an efficient or usable model for computation when
attempting to accomplish tasks on modern processors.

Using emulators in the "real world" allows for crafted binary programs to be
instrumented in dead code and, as demonstrated in
Section~\ref{subsec:decryption} encrypted and hidden. This gives an advantage to
attackers as traditional reverse engineering methods will reveal only that
emulation is being done. It reveals nothing about the ultimate goal of the
program.

To accommodate both developers as well as the unique constraints 
enforced by the speculative primitive, a custom emulation solution is required. 
We have created a custom emulator and instruction set -- SPASM -- which 
accommodate the speculative primitive specifically. This 
provides a higher level of abstraction around the speculative primitive
that we have used to implement various executable binaries.

@@

While the custom emulator that we developed gives higher level abstraction to
an author, it still requires programs to be written in a custom assembly language. 
We note that the \speculake model is not intrinsically linked to the SPASM emulator. 
A wrapper could be implemented around other existing emulators to incrementally 
construct instructions 6 or 8 bits at a time (depending on the channel width). 
This would allow for encrypted payloads to be written in higher level languages
like C or C++, although there would be a significant performance reduction to 
using this type of wrapper.

>>>>

\subsection{Virtual Machines}
We demonstrate in Section~\ref{subsec:turing} that general purpose computation 
is possible in the speculative environment in spite of the constraints 
imposed. However, a Turing Machine
is not an efficient or usable model for computation when
attempting to accomplish tasks on modern processors.

Using emulators in the ``real world'' allows for binary programs to be
placed encrypted and hidden in dead code and, as demonstrated in
Section~\ref{subsec:decryption}.
Traditional reverse engineering methods will reveal only that
emulation is being done, while the program being emulated remains encrypted.
Even when the trigger is running, only the parts of the code that execute would
be revealed to a careful analyst observing the CPU's committed state, and the
remainder of the emulated program would remain hidden.

We design a custom emulator and instruction set---SPASM (Speculative
Assembly)---that accommodates the constraints of the speculative primitive.
SPASM is a 6-bit Instruction set, where all instructions (including operand,
registers, and arguments) fit within 6-bits. This allows each step of the
speculative world to emit a single SPASM instruction to the real world for
emulation by a light-weight SPASM emulator. Using SPASM, developers can write
programs, and assemble and encrypt them into a payload program. When the
associated trigger program runs, the payload will decrypt SPASM instructions in
the speculative world, and execute them one at a time.

@@

While the custom emulator that we developed gives higher level abstraction to
an author, it still requires programs to be written in a custom assembly language. 
We note that the \speculake model is not intrinsically linked to the SPASM emulator. 
A wrapper could be implemented around other existing emulators to construct
instructions incrementally through the fixed-width channel (e.g. using 4 8-bit
reads to reveal a single 32-bit ARM instruction).
This would allow for encrypted payloads to be written in higher level languages
like C or C++, and compiled to any target architecture the real-world emulator
can execute.
